Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
typos and citations

\title{Describing the C-space of asynchronous periodic task using DIT}

@@

			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ to the formulation).\\

@@

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding a synchronous instant of
		this system (an instant at which all tasks release a job simultaneously), but
		with weaker constraints. That is, the FPDIT is an instant after the last
		deadline of all tasks, but before the next arrival time of all tasks. Finding
		a synchronous instant is equivalent to finding a solution $t$ for the
		following set of constraints :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		which is very similar to an instance of the Chinese Remainer Problem (CRP). It
		is not possible to directly use a solver for the CRP (such as Gauss's
		algorithm) as in a task system, $T_i$ values could have common factors.
		However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
		without changing the solution if there is one) in order to make the problem
		solvable through applying a solution for the CRP. \\

@@

		A better method for finding the FPDIT consists in splitting Gauss's algorithm
		into two separate parts. The global structure is simply a sum of factors, each
		term being dependant on which $a_i$ value is chosen. A major speedup can
		be acheived by first computing all possible terms for each task (only one
		modular inverse must be computed per task that way) then creating all possible DIT values
		by summing the terms in all possible ways. The number of results is still
		exponential in the number of tasks, but the only operation that is repeated
		exponentially many times is now a sum.

>>>>

\title{Describing the C-Space of Asynchronous Periodic Task Systems using
Definitive Idle Times}

@@

			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ in the list of constraints).\\

@@

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding a synchronous instant of
		this system (an instant at which all tasks release a job simultaneously), but
		with weaker constraints. That is, the FPDIT is an instant after the last
		deadline of all tasks, but before the next arrival time of all tasks. Finding
		a synchronous instant is equivalent to finding a solution $t$ for the
		following set of constraints :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		which is very similar to an instance of the Chinese Remainder Problem (CRP). It
		is not possible to directly use a solver for the CRP (such as Gauss's
		algorithm \cite{gauss1965disquisitiones}) as in a task system, $T_i$ values could have common factors.
		However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
		without changing the solution if there is one) in order to make the problem
		solvable through applying a solution for the CRP. \\

@@

		A better method for finding the FPDIT consists in splitting Gauss's algorithm
		into two separate parts. The global structure is simply a sum of factors, each
		term being dependent on which $a_i$ value is chosen. A major speedup can
		be achieved by first computing all possible terms for each task (only one
		modular inverse must be computed per task that way) then creating all possible DIT values
		by summing the terms in all possible ways. The number of results is still
		exponential in the number of tasks, but the only operation that is repeated
		exponentially many times is now a sum.
